### 2018-10-29 paper.tex
Added template

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Fingerprinting
\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%%%  \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

\begin{figure}
\centering
\psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\end{figure}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2018-10-30 paper.tex
Built with outline

@@
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
+Ang Wei Ming\\
        \email{trovato@corporation.com}
@@
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
+Chan Liang Fei Jeremy\\
        \email{webmaster@marysville-ohio.com}
 % 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
+\alignauthor 
+Ong Yong Siang\\
        \email{larst@affiliation.org}
@@
 % 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
+\alignauthor 
+Tan Zhen Yong\\
        \email{lleipuner@researchlabs.org}
 % 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+\alignauthor 
+Xu Chen\\
+       \email{xuchen@u.nus.edu}
 }
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+    Device fingerprinting is a modern technique which, instead of using traditional user identifiers(e.g. cookies and local storage), leverages on existing information available from user's device.
+    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information.We analyzes the trade-off between uniqueness of the identifier generated and ease of use for authentication.
+Lastly, we also build a simple authentification system that can be reused and extended in real-world web applications.
 \end{abstract}
 
+%%% FIXME: 
+% What else can we do?
+
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+\category{H.4}{Security Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
@@
 
-\terms{Theory}
+\terms{Security}
 
@@
 \section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+- Background in terms of old cookie and local storaged based user identification techniques.
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+- The motivation and driver for a new technology: Fingerprint
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+- Intro of the technoloy, its history, and context.
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+\section{Related work}
+- A survey of related work, what has been done, cite some papers and summarize
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+\section{Fingerprint Technology}
+- How it works in general
+- A survey of the current solutions
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+\subsection{Classification}
+-  What are the different classification, and ways
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+\subsection{Fingerprint for Authentification}
+- How can fingerprint be used to enhance authentification method
+- Intro on how Authentification is done
+\subsubsection{Desired Properties}
+- What makes it a good auth system
+\subsubsection{Thread Model}
+- What can possiblity go wrong
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+\section{Fingerprint Auth Plugin}
+What we built
+\subsection{Design}
+What is the design of the system. 
+- Flow
+- Architecture. (I believe it will be easy)
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+\subsection{Implementation}
+- What are the modules, key functions, some hacky tricks
 
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
+\section{Extension}
+- What else can be done?
 
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+\section{Conclusion}
 
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
+\section{ToBeDeleted}
+just to link the bib
+\cite{Lamport:Latex}
 
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-\psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%
 % The following two commands are all you need in the
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file
@@
 % to resolve all references
+
 %
 % ACM needs 'a single self-contained file'!
+% \subsection{Type Changes and {\subsecit Special} Characters}
 % 
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
+% \subsection{Math Equations}
+% You may want to display math equations in three distinct styles:
+% inline, numbered or non-numbered display.  Each of
+% the three are discussed in the next sections.
+% 
+% \subsubsection{Inline (In-text) Equations}
+% A formula that appears in the running text is called an
+% inline or in-text formula.  It is produced by the
+% \textbf{math} environment, which can be
+% invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
+% construction or with the short form \texttt{\$. . .\$}. You
+% can use any of the symbols and structures,
+% from $\alpha$ to $\omega$, available in
+% \LaTeX\cite{Lamport:LaTeX}; this section will simply show a
+% few examples of in-text equations in context. Notice how
+% this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
+% set here in in-line math style, looks slightly different when
+% set in display style.  (See next section).
+% 
+%
+
+%
+% \subsubsection{Display Equations}
+% A numbered display equation -- one set off by vertical space
+% from the text and centered horizontally -- is produced
+% by the \textbf{equation} environment. An unnumbered display
+% equation is produced by the \textbf{displaymath} environment.
+% 
+% Again, in either environment, you can use any of the symbols
+% and structures available in \LaTeX; this section will just
+% give a couple of examples of display equations in context.
+% First, consider the equation, shown as an inline equation above:
+% \begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
+% Notice how it is formatted somewhat differently in
+% the \textbf{displaymath}
+% environment.  Now, we'll enter an unnumbered equation:
+% \begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
+% and follow it with another numbered equation:
+% \begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
+% just to demonstrate \LaTeX's able handling of numbering.
+% 
+% \subsection{Citations}
+% Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
+% conference
+% proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
+% in the Bibliography section of your
+% article will occur throughout the text of your article.
+% You should use BibTeX to automatically produce this bibliography;
+% you simply need to insert one of several citation commands with
+% a key of the item cited in the proper location in
+% the \texttt{.tex} file \cite{Lamport:LaTeX}.
+% The key is a short reference you invent to uniquely
+% identify each work; in this sample document, the key is
+% the first author's surname and a
+% word from the title.  This identifying key is included
+% with each item in the \texttt{.bib} file for your article.
+% 
+% The details of the construction of the \texttt{.bib} file
+% are beyond the scope of this sample document, but more
+% information can be found in the \textit{Author's Guide},
+% and exhaustive details in the \textit{\LaTeX\ User's
+% Guide}\cite{Lamport:LaTeX}.
+% 
+% This article shows only the plainest form
+% of the citation command, using \texttt{{\char'134}cite}.
+% This is what is stipulated in the SIGS style specifications.
+% No other citation format is endorsed.
+% 
+% \subsection{Tables}
+% Because tables cannot be split across pages, the best
+% placement for them is typically the top of the page
+% nearest their initial cite.  To
+% ensure this proper ``floating'' placement of tables, use the
+% environment \textbf{table} to enclose the table's contents and
+% the table caption.  The contents of the table itself must go
+% in the \textbf{tabular} environment, to
+% be aligned properly in rows and columns, with the desired
+% horizontal and vertical rules.  Again, detailed instructions
+% on \textbf{tabular} material
+% is found in the \textit{\LaTeX\ User's Guide}.
+% 
+% Immediately following this sentence is the point at which
+% Table 1 is included in the input file; compare the
+% placement of the table here with the table in the printed
+% dvi output of this document.
+% 
+% \begin{table}
+% \centering
+% \caption{Frequency of Special Characters}
+% \begin{tabular}{|c|c|l|} \hline
+% Non-English or Math&Frequency&Comments\\ \hline
+% \O & 1 in 1,000& For Swedish names\\ \hline
+% $\pi$ & 1 in 5& Common in math\\ \hline
+% \$ & 4 in 5 & Used in business\\ \hline
+% $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+% \hline\end{tabular}
+% \end{table}
+% 
+% To set a wider table, which takes up the whole width of
+% the page's live area, use the environment
+% \textbf{table*} to enclose the table's contents and
+% the table caption.  As with a single-column table, this wide
+% table will ``float" to a location deemed more desirable.
+% Immediately following this sentence is the point at which
+% Table 2 is included in the input file; again, it is
+% instructive to compare the placement of the
+% table here with the table in the printed dvi
+% output of this document.
+% 
+% 
+% \begin{table*}
+% \centering
+% \caption{Some Typical Commands}
+% \begin{tabular}{|c|c|l|} \hline
+% Command&A Number&Comments\\ \hline
+% \texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
+% \texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
+% \texttt{{\char'134}table}& 300 & For tables\\ \hline
+% \texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
+% \end{table*}
+% % end the environment with {table*}, NOTE not {table}!
+% 
+% \subsection{Figures}
+% Like tables, figures cannot be split across pages; the
+% best placement for them
+% is typically the top or the bottom of the page nearest
+% their initial cite.  To ensure this proper ``floating'' placement
+% of figures, use the environment
+% \textbf{figure} to enclose the figure and its caption.
+% 
+% This sample document contains examples of \textbf{.eps}
+% and \textbf{.ps} files to be displayable with \LaTeX.  More
+% details on each of these is found in the \textit{Author's Guide}.
+% 
+% \begin{figure}
+% \centering
+% \epsfig{file=fly.eps}
+% \caption{A sample black and white graphic (.eps format).}
+% \end{figure}
+% 
+% \begin{figure}
+% \centering
+% \epsfig{file=fly.eps, height=1in, width=1in}
+% \caption{A sample black and white graphic (.eps format)
+% that has been resized with the \texttt{epsfig} command.}
+% \end{figure}
+% 
+% 
+% As was the case with tables, you may want a figure
+% that spans two columns.  To do this, and still to
+% ensure proper ``floating'' placement of tables, use the environment
+% \textbf{figure*} to enclose the figure and its caption.
+% 
+% Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
+% used; use
+% the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
+% commands as appropriate for the different file types.
+% 
+% \subsection{Theorem-like Constructs}
+% Other common constructs that may occur in your article are
+% the forms for logical constructs like theorems, axioms,
+% corollaries and proofs.  There are
+% two forms, one produced by the
+% command \texttt{{\char'134}newtheorem} and the
+% other by the command \texttt{{\char'134}newdef}; perhaps
+% the clearest and easiest way to distinguish them is
+% to compare the two in the output of this sample document:
+% 
+% This uses the \textbf{theorem} environment, created by
+% the\linebreak\texttt{{\char'134}newtheorem} command:
+% \newtheorem{theorem}{Theorem}
+% \begin{theorem}
+% Let $f$ be continuous on $[a,b]$.  If $G$ is
+% an antiderivative for $f$ on $[a,b]$, then
+% \begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
+% \end{theorem}
+% 
+% The other uses the \textbf{definition} environment, created
+% by the \texttt{{\char'134}newdef} command:
+% \newdef{definition}{Definition}
+% \begin{definition}
+% If $z$ is irrational, then by $e^z$ we mean the
+% unique number which has
+% logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
+% \end{definition}
+% 
+% \begin{figure}
+% \centering
+% \psfig{file=rosette.ps, height=1in, width=1in,}
+% \caption{A sample black and white graphic (.ps format) that has
+% been resized with the \texttt{psfig} command.}
+% \end{figure}
+% 
+% Two lists of constructs that use one of these
+% forms is given in the
+% \textit{Author's  Guidelines}.
+% 
+% \begin{figure*}
+% \centering
+% \epsfig{file=flies.eps}
+% \caption{A sample black and white graphic (.eps format)
+% that needs to span two columns of text.}
+% \end{figure*}
+% and don't forget to end the environment with
+% {figure*}, not {figure}!
+%  
+% There is one other similar construct environment, which is
+% already set up
+% for you; i.e. you must \textit{not} use
+% a \texttt{{\char'134}newdef} command to
+% create it: the \textbf{proof} environment.  Here
+% is a example of its use:
+% \begin{proof}
+% Suppose on the contrary there exists a real number $L$ such that
+% \begin{displaymath}
+% \lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
+% \end{displaymath}
+% Then
+% \begin{displaymath}
+% l=\lim_{x\rightarrow c} f(x)
+% = \lim_{x\rightarrow c}
+% \left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
+% = \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
+% \frac{f(x)}{g(x)} = 0\cdot L = 0,
+% \end{displaymath}
+% which contradicts our assumption that $l\neq 0$.
+% \end{proof}
+% 
+% Complete rules about using these environments and using the
+% two different creation commands are in the
+% \textit{Author's Guide}; please consult it for more
+% detailed instructions.  If you need to use another construct,
+% not listed therein, which you want to have the same
+% formatting as the Theorem
+% or the Definition\cite{salas:calculus} shown above,
+% use the \texttt{{\char'134}newtheorem} or the
+% \texttt{{\char'134}newdef} command,
+% respectively, to create it.
+% 
+% \subsection*{A {\secit Caveat} for the \TeX\ Expert}
+% Because you have just been given permission to
+% use the \texttt{{\char'134}newdef} command to create a
+% new form, you might think you can
+% use \TeX's \texttt{{\char'134}def} to create a
+% new command: \textit{Please refrain from doing this!}
+% Remember that your \LaTeX\ source code is primarily intended
+% to create camera-ready copy, but may be converted
+% to other forms -- e.g. HTML. If you inadvertently omit
+% some or all of the \texttt{{\char'134}def}s recompilation will
+% be, to say the least, problematic.
+% 
+% \section{Conclusions}
+% This paragraph will end the body of this sample document.
+% Remember that you might still have Acknowledgments or
+% Appendices; brief samples of these
+% follow.  There is still the Bibliography to deal with; and
+% we will make a disclaimer about that here: with the exception
+% of the reference to the \LaTeX\ book, the citations in
+% this paper are to articles which have nothing to
+% do with the present subject and are used as
+% examples only.
+% %\end{document}  % This is where a 'short' article might terminate
+% 
+% %ACKNOWLEDGMENTS are optional
+% \section{Acknowledgments}
+% This section is optional; it is a location for you
+% to acknowledge grants, funding, editing assistance and
+% what have you.  In the present case, for example, the
+% authors would like to thank Gerald Murray of ACM for
+% his help in codifying this \textit{Author's Guide}
+% and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+% %APPENDICES are optional
+% %\balancecolumns
+% \appendix
+% %Appendix A
+% \section{Headings in Appendices}
+% The rules about hierarchical headings discussed above for
+% the body of the article are different in the appendices.
+% In the \textbf{appendix} environment, the command
+% \textbf{section} is used to
+% indicate the start of each Appendix, with alphabetic order
+% designation (i.e. the first is A, the second B, etc.) and
+% a title (if you include one).  So, if you need
+% hierarchical structure
+% \textit{within} an Appendix, start with \textbf{subsection} as the
+% highest level. Here is an outline of the body of this
+% document in Appendix-appropriate form:
+% \subsection{Introduction}
+% \subsection{The Body of the Paper}
+% \subsubsection{Type Changes and  Special Characters}
+% \subsubsection{Math Equations}
+% \paragraph{Inline (In-text) Equations}
+% \paragraph{Display Equations}
+% \subsubsection{Citations}
+% \subsubsection{Tables}
+% \subsubsection{Figures}
+% \subsubsection{Theorem-like Constructs}
+% \subsubsection*{A Caveat for the \TeX\ Expert}
+% \subsection{Conclusions}
+% \subsection{Acknowledgments}
+% \subsection{Additional Authors}
+% This section is inserted by \LaTeX; you do not insert it.
+% You just add the names and information in the
+% \texttt{{\char'134}additionalauthors} command at the start
+% of the document.
+% \subsection{References}
+% Generated by bibtex from your ~.bib file.  Run latex,
+% then bibtex, then latex twice (to resolve references)
+% to create the ~.bbl file.  Insert that ~.bbl file into
+% the .tex source file and comment out
+% the command \texttt{{\char'134}thebibliography}.
 % This next section command marks the start of
 % Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
+% \section{More Help for the Hardy}
+% The acm\_proc\_article-sp document class file itself is chock-full of succinct
+% and helpful comments.  If you consider yourself a moderately
+% experienced to expert user of \LaTeX, you may find reading
+% it useful but please remember not to change it.
+% \balancecolumns
+% % That's all folks!
 \end{document}

### 2018-11-08 paper.tex
Done Fingerprint tech part with reference

@@
 - Background in terms of old cookie and local storaged based user identification techniques.
-
 - The motivation and driver for a new technology: Fingerprint
@@
 \section{Fingerprint Technology}
-- How it works in general
-- A survey of the current solutions
 
-\subsection{Classification}
--  What are the different classification, and ways
+\subsection{Overview of the Fingerprinting Practices}
+Browser fingerprinting technology usually involves the process of collecting user data from various level of the device, such as user's browser information and the operating system information.
+\cite{pierre:beauty}
+In contrast with the state-of-the-art Cookies methodology, such fingerprinting is said to be "stateless" because no additional information (e.g., cookies, tokens) is stored on the user's device.
+
+With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by emplanting scripts that collect and process those information into the web page, as shown by Nikiforaskis.
+Eckersley from Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies.
+Almost 500K browsers have their information scanned and recorded on the Panopticlick website, and around $83.6\%$ of them can be identified uniquely.
+More recently, newer techniques are discovered that exploit the potential issues in JavaScript engine to reveal more information such as operating system and microarchitecture, even hardware information such as screen resolution.
+\cite{mowery:fg} \cite{boda:user}
+As HTML5 and WebGL becomes more popular tools at rendering web sites content, new fingerprinting information is added to the arsenal.
+More importantly, such fingerprinting information is no longer restricted to browser properties because different hardware and softwares will behave differently when rendering images through the canvas component.\cite{mowery:pixel}
+
+Contrary to the common notion of information leaking, none of the above-mentioned practices involves complicated mechanism such as password hacking, or any sort of attack.
+This information is just available.
+The underlying reason that so much fine-grained information about the browser and the user can be retrieved is the necessity for a web application to be able to render the pages based on differnt devices effectively.
+Responsive web application needs to know the dimension of the screen; a video application might need to know the presence of plugin like Adobe Flash.
+In order to serve various demands, the browser expose APIs for developers to query such information, e.g., the built-in \verb|navigator| and \verb|screen| objects from Javascript which reveals the browser name, version, platform information.
+In addition, browser plugins, softwares from third-party which add in many enriching features to the browser have access to information about the computers, that can expose more accurate identifiers.
+
+\subsection{Surveys of Fingerprinting Practices}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{assets/amiunique.png}
+    \caption{List of Attributes Fingerprinted for AmIUnique.org}
+    \label{fig:amiunique}
+\end{figure*}
+
+According to Acar et al.
+\cite{acar:fpd}, browser fingerprinting technologies can be categorized by the approach they collect information: (1) JavasScript-based, (2) Plugin-based, (3) Extension-based, (4) Header-based and Server-side.
+The rest of this seciton will go through in more details about each of them.
+
+\paragraph{JavaScript-Based Fingerprinting}
+JavaScript is the default scripting language for almost all interactive web applications now.
+It provides functionalities such as rendering of animation, submitting of user forms, and altering the content of the page dynamically.
+Other than the informative objects mentioned earlier (\verb|navigator| and \verb|screen|), JavaScript can also be used to identify users indirectly, such as obtaining the information of the browsing history, the nuances in performance of JavaScript engine at different browsers.
+
+\paragraph{Plugin-Based Fingerprinting}
+Plugins nowadays are equipped with capabilities to access the software and hardware properties on the underlying system.
+One of these common plugins is Flash, that is used for displaying videos and games in the \verb|.swf| format.
+In order for the web pages to use Flash effectively, Flash exposes APIs to query for the information on the operating system, as well as the specific version of Flash being installed.
+Moreover, Flash also exposes APIs that allow one to list all the system fonts, which can vary from users to users.
+The difference in those fonts installed can again be used as an identifier for the user.
+Therefore, the more plugins a user installed, the more information that those plugins expose to fingerprinters.
+
+\paragraph{Extension-Based Fingerprinting}
+A browser extension is a special software component that adds extra functionalities to the browsers, just like how one can download additional applications from an App Store.
+Common extensions are like RSS feeders, Evernote, etc.
+They are different from plugins as extensions provide additional functionalities to the browser while plugins enable some functionalities so that web page can be rendered effectively.
+Take one of the extensions that expose additional
+information as an example: \verb|NoScript| \cite{noscript}, which is an extension that blocks executions of Web objects from any URL but those whitelisted.
+As explained by Mowery et al.
+\cite{mowery:fg}, one can prepare a list of URLs in the web page and see which of them are listed on the whitelist.
+The whitelist of the extension then can be used as an identifier to differentiate users from each other.
+
+\paragraph{Header-Based and Server-Side}
+This is one of the most original fingerprinting practice where the fingerprinters use information from the HTTP headers as identifiers.
+The HTTP headers contain information such as th IP address, HTTP Accept Headers, and etc every time in the request.
+Such information is readily avaialble for all the websites and sent to the servers in the HTTP request.
+
+Combining all these different practices together, the fingerprinter can obtain lots of information about the user.
+Laperdrix et al.
+\cite{pierre:beauty} demonstrates that one can come up with 17 attributes from various channels to idenfity fingerprints for mobile users.
+As shown in Figure \ref{fig:amiunique}, the possible number of combinations of the different vlaues from those parameters is rather large, and the study successfully identify $81\%$ users out of 118,000 users.
 
 \subsection{Fingerprint for Authentification}
-- How can fingerprint be used to enhance authentification method
-- Intro on how Authentification is done
+Despite the enumerous security loopholes in password-based authentification methodology, it still remains the dominant way for web authentification currently.
+There are multiple ways to enhance the security of password-based authentification, such as the Multi-Factor Authentification model.
+Fingerprinting technology can be used as the supporting method of authentification to augment the traditional password-based method.
+A number of commercial fraud detection services have already started trying using device fingerprinting to identify fraudulent transactions.\cite{maxmind} \cite{parame} Fingerprints about user's device is collected implicitly and stored alongside with the contentional password for a user without user's intervention.
+The server can use a wide range of fingerprinting methods described in the early sections .The servers can then verify such information later when user is authenticated.
+
+The following sections will descuss the possible attacks where device fingerprinting can be used to strengthen web authentification.
+
 \subsubsection{Desired Properties}
-- What makes it a good auth system
-\subsubsection{Thread Model}
-- What can possiblity go wrong
+In order to effectivley augment user authentification with fingerprinting, there are obviously certain properties of the fingerprinting practices used that must be held to make authentification safer and easier.
+A set of inappropriate fingerprinting practices chosen may incur too many false negatives in authentification process, denying users access or falling back to the most conservative authentification process frequently.
+Comparing to the general usage of fingeprinting in advertising, fingerprinting for authentification requires a higher level of accuracy in distinguishing users.
+A $80\%$ or $90\%$ is simply not enough.
+\cite{alca:dev}
+
+In this section, we will be descussing the properties that make a set of fingerprinting practices a good augmentation for the authentification process:
+
+\paragraph{ Stablility at Different Occasions}
+It is normal for a user to have his/her fingerprint changes over time or at different occassions. For example, traveling to different time zones, or switching of devices for various works at school. 
+A significant change in the device fingerprints will usually lead to the falling back to a less convenient but reliable authentification process, such as one-time code sent to the phone or email.
+Therefore, using fingerprint practices that are reliable over the time for a particular user is prefereable.
+Having more and diverse metrics collected from different fingerprint practices will allow a small subset of values to varify without decreasing the overall stability of the
+fingerprint.
+
+\paragraph{ Repeatability on Same Device }
+Repeatability is defined as a peroperty whereby the same fingerprint practices generate the same results if the software, hardware, and network configuration of a device does not change.
+\cite{alca:dev}.
+It is related to but different from the stability requirement, which it primarily concerns changes in the device configuration.
+For some particular fingerprint practices, such as measuring the JavaScript rendering performance (determined and related to the underlying GPU/CPU performance and load at a specific instance), the same device may generate different results with other applications running: for example, trying to login when having a video compliation job running in the background might produce different fingerprint.
+
+\paragraph { Resistence to Spoofing}
+An attacker can potentially spoof a device fingerprint by mimicing the properties or behaviour of the targeted device.
+Certain fingerprinting practices will then have a low threshold for this kind of spoofing attack.
+For example, if the server relies on running a particular JavaScript script at the client side and retrieves the result from the client, then an attack can potentially replay the results to pretend to be the victim.
+On the other hand, some fingerprint practices are more resistent to such spoofing, such as IP address of the sources\cite{beverly:ip}, the timestamps indicating clock skew from MAC protocols packets \cite{ara:wire}.
+
+There are many other requirements that are not listed above in details, such as the overheads in fingerprint collection, the convenience and level of action required from the user, and personalized identification information (the unqiueness of the fingerprints).
+
+\subsubsection{Fingerprint Authentification Solution}
+In this section, we discuss two strategies of using fingerprinting to augment authentification: (1) fingerprinting at session initialization, (2) fingerprinting throughout an authenticated session.
+
+\paragraph{Fingerprint at the start of session}
+Fingerprint information is used as an additional authentification dimension alongside the normal password-based authentification (or other primary authentification method), and an authenticated session requires the matching of both the primary response as well as the fingerprint data stored.
+In order for this strategy to work, the server must be able to store persistently the fingerprint data which is given by the user at registration. 
+Such strategy can go hand-in-hand with the current two-factor authentification.
+For example, in the event where the device used for receiving SMS is stolen, fingerprint of the stolen device might reveal the unsual state of it as the fingerprint check failed, which leads to additional security checks.
+
+In general, the strategy can prevent or make the below attack more difficult: 
+\begin{itemize}
+    \item \textbf{Naive Attack} A naive attack is defined as a conventional password-guessing attack that does not attempt to provide a matching fingerprint.
+Device fingerprint can effectively counter this attack since the attacker is assumed to launch the attack in a rather different environment.
+    \item \textbf{Optimized Password and Fingerprint Guessing}: The attacker might prepare a common profile of fingerprint and uses the popular profile of fingerprint to launch a naive attack by guess the passwords.
+Device fingerprint can effectively reduce the chance of success under this attack given that the fingeprint information expands the guessing space, and the attacker is only allowed with limited number of trials.
+    \item \textbf{Fingerprint Spoofing and Phishing}: Just like the normal password spoofing and phishing attack, the attacker can collect fingerprint information from users on top of the password.
+The level of spoofing resistence used in fingerprint will then largely determine the feasibility of this attack.
+\end{itemize}
+
+\paragraph{Fingerprint throughout an authenticated session}
+In a typical password-based web authentication scheme, the server will return a cookie upon receiving a valid username and password so that the client will use the cookie as a proof of authentication in every request later on.
+This could be strenghened by validating the fingerprint information at each request.
+If the set of fingerprints that the server collect is static, the recomputation of the fingerprint at each request is redundant.
+
+A simple replay attack can be effecively prevented by hashing the fingerprint at the client with a counter before sending to the server, as demonstrated by \cite{preu:smart}.
+However, for a more powerful attack such as XSS attack, it is less effective.
+The attacker can launch a XSS targeted at the victim, and steal the plaintext device fingerprint and the counter at the client-side.
+Once obtaining the fingerprint plaintext, the attacker can reproduce the hash by increment the counter
+and recomputing.
+In addition, such XSS hijack attack is also possible even if the server dynamically changes the set of fignerprint in each request \cite{unger:shpf} as the attacker can simply collect additional information about the target device once hijack is sucessful.
 
@@
 \section{Conclusion}
-
-\section{ToBeDeleted}
-just to link the bib
-\cite{Lamport:Latex}
 

### 2018-11-08 paper.tex
Add author name and email
Fix typos in abstract

@@
 Tan Zhen Yong\\
-       \email{lleipuner@researchlabs.org}
+       \email{tan.zhenyong@u.nus.edu}
 % 5th. author
@@
 \begin{abstract}
-    Device fingerprinting is a modern technique which, instead of using traditional user identifiers(e.g. cookies and local storage), leverages on existing information available from user's device.
-    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information.We analyzes the trade-off between uniqueness of the identifier generated and ease of use for authentication.
-Lastly, we also build a simple authentification system that can be reused and extended in real-world web applications.
+    Device fingerprinting is a modern technique which, instead of using traditional user identifiers (e.g. cookies and local storage), leverages on existing information available from user's device.
+    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information.
+We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication.
+Lastly, we also build a simple authentication system that can be reused and extended in real-world web applications.
 \end{abstract}

### 2018-11-08 paper.tex
Add categories and subject descriptors

@@
 % A category with the (minimum) three required fields
-\category{H.4}{Security Systems Applications}{Miscellaneous}
+\category{C.2.0}{Computer-Communication Networks}{General}---\textit{Security and Protection}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\category{D.4.6}{Operating Systems}{Security and Protection}---\textit{Authentication}
+\category{K.6.5}{Management of Computing and Information Systems}{Security and Protection}---\textit{Authentication}
 

### 2018-11-08 paper.tex
Add some keywords
Fix typos and language for fingerprinting overview

@@
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+\keywords{Authentication, device fingerprinting, web authentication} % NOT required for Proceedings
 
@@
 With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by emplanting scripts that collect and process those information into the web page, as shown by Nikiforaskis.
-Eckersley from Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies.
+Eckersley from the Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies.
 Almost 500K browsers have their information scanned and recorded on the Panopticlick website, and around $83.6\%$ of them can be identified uniquely.
-More recently, newer techniques are discovered that exploit the potential issues in JavaScript engine to reveal more information such as operating system and microarchitecture, even hardware information such as screen resolution.
+More recently, newer techniques have been discovered that use JavaScript to reveal more information such as operating system and microarchitecture, and even hardware information such as screen resolution.
 \cite{mowery:fg} \cite{boda:user}
-As HTML5 and WebGL becomes more popular tools at rendering web sites content, new fingerprinting information is added to the arsenal.
-More importantly, such fingerprinting information is no longer restricted to browser properties because different hardware and softwares will behave differently when rendering images through the canvas component.\cite{mowery:pixel}
+As HTML5 and WebGL becomes more popular tools for websites, new sources of fingerprinting information is added to the arsenal.
+More importantly, such fingerprinting information is no longer restricted to browser properties because different system configurations will behave differently when rendering images through the canvas component.\cite{mowery:pixel}
 
-Contrary to the common notion of information leaking, none of the above-mentioned practices involves complicated mechanism such as password hacking, or any sort of attack.
-This information is just available.
-The underlying reason that so much fine-grained information about the browser and the user can be retrieved is the necessity for a web application to be able to render the pages based on differnt devices effectively.
-Responsive web application needs to know the dimension of the screen; a video application might need to know the presence of plugin like Adobe Flash.
-In order to serve various demands, the browser expose APIs for developers to query such information, e.g., the built-in \verb|navigator| and \verb|screen| objects from Javascript which reveals the browser name, version, platform information.
-In addition, browser plugins, softwares from third-party which add in many enriching features to the browser have access to information about the computers, that can expose more accurate identifiers.
+Contrary to the common notion of information leaking, none of the above-mentioned practices involves complicated mechanisms such as password hacking, or any sort of attack.
+The is because so much fine-grained information about the browser and the user can be retrieved as a necessity for web applications to be able to serve content based on different devices effectively.
+For example, responsive web applications need to know the dimension of the screen, while a video streaming service may need to know the presence of plugins like Adobe Flash.
+In order to serve these various demands, the browser expose APIs for developers to query such information, e.g., the built-in \verb|navigator| and \verb|screen| objects in JavaScript which reveal the browser name, version, platform information.
+In addition, browser plugins which add  features to the browser also have access to information about the computer that can expose more accurate identifiers.
 

### 2018-11-08 paper.tex
Fix typos and language for fingerprinting survey

@@
 
-\subsection{Surveys of Fingerprinting Practices}
+\subsection{Survey of Fingerprinting Practices}
 
@@
 According to Acar et al.
-\cite{acar:fpd}, browser fingerprinting technologies can be categorized by the approach they collect information: (1) JavasScript-based, (2) Plugin-based, (3) Extension-based, (4) Header-based and Server-side.
-The rest of this seciton will go through in more details about each of them.
+\cite{acar:fpd}, browser fingerprinting technologies can be categorized by the approach they use to collect information: (1) JavaScript-based, (2) Plugin-based, (3) Extension-based, (4) Header-based and Server-side.
+The rest of this section will go through in more details about each of them.
 
@@
 JavaScript is the default scripting language for almost all interactive web applications now.
-It provides functionalities such as rendering of animation, submitting of user forms, and altering the content of the page dynamically.
-Other than the informative objects mentioned earlier (\verb|navigator| and \verb|screen|), JavaScript can also be used to identify users indirectly, such as obtaining the information of the browsing history, the nuances in performance of JavaScript engine at different browsers.
+It provides functionality such as rendering of animation, submitting of user forms, and altering the content of the page dynamically.
+Other than the informative objects mentioned earlier (\verb|navigator| and \verb|screen|), JavaScript can also be used to identify users indirectly, such as obtaining  browsing history or fine-grained timing information of the JavaScript engine at different browsers.
 
 \paragraph{Plugin-Based Fingerprinting}
-Plugins nowadays are equipped with capabilities to access the software and hardware properties on the underlying system.
-One of these common plugins is Flash, that is used for displaying videos and games in the \verb|.swf| format.
-In order for the web pages to use Flash effectively, Flash exposes APIs to query for the information on the operating system, as well as the specific version of Flash being installed.
-Moreover, Flash also exposes APIs that allow one to list all the system fonts, which can vary from users to users.
+Plugins are equipped with capabilities to access the software and hardware properties of the underlying system.
+One of these common plugins is Flash that is used for displaying videos and games in the \verb|.swf| format.
+In order for the web pages to use Flash effectively, Flash exposes APIs to query  information about the operating system, as well as the specific version of Flash installed.
+Moreover, Flash also exposes APIs that allow one to list all the system fonts, which can vary from user to user.
 The difference in those fonts installed can again be used as an identifier for the user.
-Therefore, the more plugins a user installed, the more information that those plugins expose to fingerprinters.
+Therefore, the more plugins a user has installed, the more information can be exposed to fingerprinting software.
 
 \paragraph{Extension-Based Fingerprinting}
-A browser extension is a special software component that adds extra functionalities to the browsers, just like how one can download additional applications from an App Store.
-Common extensions are like RSS feeders, Evernote, etc.
-They are different from plugins as extensions provide additional functionalities to the browser while plugins enable some functionalities so that web page can be rendered effectively.
+A browser extension is a special software component that adds extra functionality to the browser, such as RSS reader or ad-blockers.
+Extensions are different from plugins as extensions provide additional functionality in the browser itself while plugins enable additional functionality for rendering a web page.
 Take one of the extensions  that expose additional
@@
 \paragraph{Header-Based and Server-Side}
-This is one of the most original fingerprinting practice where the fingerprinters use information from the HTTP headers as identifiers.
-The HTTP headers contain information such as th IP address, HTTP Accept Headers, and etc every time in the request.
-Such information is readily avaialble for all the websites and sent to the servers in the HTTP request.
+This is one of the most basic fingerprinting techniques where the fingerprinters use information from the HTTP headers as identifiers.
+The HTTP headers contain information such as the IP address or Accept Headers in the request.
+Such information is readily available for all browsers and sent to  servers in the HTTP request.
 
-Combining all these different practices together, the fingerprinter can obtain lots of information about the user.
+Combining all these different practices together, the fingerprinter can obtain a large amount of information on a user.
 Laperdrix et al.
-\cite{pierre:beauty} demonstrates that one can come up with 17 attributes from various channels to idenfity fingerprints for mobile users.
-As shown in Figure \ref{fig:amiunique}, the possible number of combinations of the different vlaues from those parameters is rather large, and the study successfully identify $81\%$ users out of 118,000 users.
+\cite{pierre:beauty} demonstrates that one can combine at least 17 attributes from various sources to create unique device fingerprints.
+As shown in Figure \ref{fig:amiunique}, the possible number of combinations of the different vlaues from those parameters is rather large, and the study successfully identified $81\%$ users out of 118,000 users.
 

### 2018-11-08 paper.tex
s/fingerprint practices/fingerprint techniques/g

@@
 
-\subsection{Overview of the Fingerprinting Practices}
+\subsection{Overview of  Fingerprinting Techniques}
 Browser fingerprinting technology usually involves the process of collecting user data from various level of the device, such as user's browser information and the operating system information.
@@
 
-With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by emplanting scripts that collect and process those information into the web page, as shown by Nikiforaskis.
+With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by embedding scripts that collect and process those information into the web page, as shown by Nikiforaskis.
 Eckersley from the Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies.
@@
 
-\subsection{Survey of Fingerprinting Practices}
+\subsection{Survey of Fingerprinting Techniques}
 

### 2018-11-08 paper.tex
Correct minor typo in fingerprint technique survey
Fix typos and language in fingerprinting for authentication

@@
 \cite{acar:fpd}, browser fingerprinting technologies can be categorized by the approach they use to collect information: (1) JavaScript-based, (2) Plugin-based, (3) Extension-based, (4) Header-based and Server-side.
-The rest of this section will go through in more details about each of them.
+The rest of this section will go through in more detail about each of them.
 
@@
 
-\subsection{Fingerprint for Authentification}
-Despite the enumerous security loopholes in password-based authentification methodology, it still remains the dominant way for web authentification currently.
-There are multiple ways to enhance the security of password-based authentification, such as the Multi-Factor Authentification model.
-Fingerprinting technology can be used as the supporting method of authentification to augment the traditional password-based method.
-A number of commercial fraud detection services have already started trying using device fingerprinting to identify fraudulent transactions.\cite{maxmind} \cite{parame} Fingerprints about user's device is collected implicitly and stored alongside with the contentional password for a user without user's intervention.
-The server can use a wide range of fingerprinting methods described in the early sections .The servers can then verify such information later when user is authenticated.
+\subsection{Fingerprinting for Authentication}
+Despite the existing shortcomings of a password-based authentication methodology, it still remains the dominant method for web authentication.
+There are multiple ways to enhance the security of password-based authentication, such as the Multi-Factor Authentication model.
+Device fingerprinting can also be used to augment password-based authentication.
+A number of commercial fraud detection services have already started using device fingerprinting in identifying fraudulent transactions.\cite{maxmind} \cite{parame} A user's device fingerprint is collected automatically and stored alongside their\ password.
+The server can use a wide range of fingerprinting methods such as those described in earlier.
+The server can then verify the device fingerprint later during authentication.
 
-The following sections will descuss the possible attacks where device fingerprinting can be used to strengthen web authentification.
+The following sections will discuss the areas to consider when device fingerprinting is used to strengthen web authentication.
 
 \subsubsection{Desired Properties}
-In order to effectivley augment user authentification with fingerprinting, there are obviously certain properties of the fingerprinting practices used that must be held to make authentification safer and easier.
-A set of inappropriate fingerprinting practices chosen may incur too many false negatives in authentification process, denying users access or falling back to the most conservative authentification process frequently.
-Comparing to the general usage of fingeprinting in advertising, fingerprinting for authentification requires a higher level of accuracy in distinguishing users.
-A $80\%$ or $90\%$ is simply not enough.
+In order to effectively augment user authentication with device fingerprinting, there are a number of properties that the device fingerprint should hold.
+A set of inappropriate fingerprinting practices may incur too many false negatives in the authentication process, denying legitimate users access or falling back to the most conservative authentication process too frequently.
+Compared to the general usage of fingeprinting in advertising, fingerprinting for authentication requires a higher level of accuracy in distinguishing users.
+A $80\%$ or $90\%$ accuracy is simply not enough.
 \cite{alca:dev}
 
-In this section, we will be descussing the properties that make a set of fingerprinting practices a good augmentation for the authentification process:
+In this section, we will be discussing the properties that make a set of fingerprinting practices a good augmentation for the authentication process:
 
-\paragraph{ Stablility at Different Occasions}
-It is normal for a user to have his/her fingerprint changes over time or at different occassions. For example, traveling to different time zones, or switching of devices for various works at school. 
-A significant change in the device fingerprints will usually lead to the falling back to a less convenient but reliable authentification process, such as one-time code sent to the phone or email.
-Therefore, using fingerprint practices that are reliable over the time for a particular user is prefereable.
-Having more and diverse metrics collected from different fingerprint practices will allow a small subset of values to varify without decreasing the overall stability of the
-fingerprint.
+\paragraph{Stablility across different scenarios}
+It is normal for a user to have their device fingerprint change over time or in different scenarios. For example,  a user may be traveling across different time zones or switch between devices. 
+A significant change in the device fingerprints will usually lead to a fallback on a less convenient but reliable authentication process, such as a one-time code sent to the user's phone or email.
+Therefore, using fingerprint practices that are reliable over time for a particular user is prefereable.
+Having more diverse metrics collected from different fingerprint practices will allow a small subset of values to vary without decreasing the overall stability of the fingerprint.
 
-\paragraph{ Repeatability on Same Device }
-Repeatability is defined as a peroperty whereby the same fingerprint practices generate the same results if the software, hardware, and network configuration of a device does not change.
+\paragraph{Repeatability on same device}
+Repeatability is defined as the property whereby the same fingerprinting techniques generate the same results if the software, hardware, and network configuration of a device does not change.
 \cite{alca:dev}.
-It is related to but different from the stability requirement, which it primarily concerns changes in the device configuration.
-For some particular fingerprint practices, such as measuring the JavaScript rendering performance (determined and related to the underlying GPU/CPU performance and load at a specific instance), the same device may generate different results with other applications running: for example, trying to login when having a video compliation job running in the background might produce different fingerprint.
+It is related to but different from the stability requirement, which is primarily concerned  with changes in the device configuration.
+For some  fingerprinting techniques, such as measuring the JavaScript rendering performance (determined and related to the underlying GPU/CPU performance and load at a specific instance), the same device may generate different results with other applications running: for example, trying to login when having a video compliation job running in the background might produce different fingerprints.
 
-\paragraph { Resistence to Spoofing}
-An attacker can potentially spoof a device fingerprint by mimicing the properties or behaviour of the targeted device.
-Certain fingerprinting practices will then have a low threshold for this kind of spoofing attack.
-For example, if the server relies on running a particular JavaScript script at the client side and retrieves the result from the client, then an attack can potentially replay the results to pretend to be the victim.
-On the other hand, some fingerprint practices are more resistent to such spoofing, such as IP address of the sources\cite{beverly:ip}, the timestamps indicating clock skew from MAC protocols packets \cite{ara:wire}.
+\paragraph {Resistence to spoofing}
+An attacker can potentially spoof a device fingerprint by mimicking the properties or behaviour of the targeted device.
+Some fingerprinting techniques  have a low threshold for this kind of spoofing attack.
+For example, if the server relies on running a particular JavaScript script at the client side and retrieving the result from the client, then an attack can potentially replay the results to pretend to be the victim.
+On the other hand, some fingerprint technique are more resistent to such spoofing, such as the IP address of the sources\cite{beverly:ip} or timestamps indicating clock skew from MAC protocol packets \cite{ara:wire}.
 
-There are many other requirements that are not listed above in details, such as the overheads in fingerprint collection, the convenience and level of action required from the user, and personalized identification information (the unqiueness of the fingerprints).
+There are many other requirements that are not listed above in detail, such as the overhead in fingerprint collection, the convenience and level of action required from the user, and personalized identification information (the uniqueness of the fingerprints).
 
-\subsubsection{Fingerprint Authentification Solution}
-In this section, we discuss two strategies of using fingerprinting to augment authentification: (1) fingerprinting at session initialization, (2) fingerprinting throughout an authenticated session.
+\subsubsection{Fingerprint Authentication Solution}
+In this section, we discuss two strategies of using fingerprinting to augment authentication: (1) fingerprinting at session initialization, (2) fingerprinting throughout an authenticated session.
 
 \paragraph{Fingerprint at the start of session}
-Fingerprint information is used as an additional authentification dimension alongside the normal password-based authentification (or other primary authentification method), and an authenticated session requires the matching of both the primary response as well as the fingerprint data stored.
+Fingerprint information is used as an additional authentication dimension alongside the normal password-based authentication (or other primary authentication method), and an authenticated session requires the matching of both the primary response as well as the fingerprint data stored.
 In order for this strategy to work, the server must be able to store persistently the fingerprint data which is given by the user at registration. 
-Such strategy can go hand-in-hand with the current two-factor authentification.
-For example, in the event where the device used for receiving SMS is stolen, fingerprint of the stolen device might reveal the unsual state of it as the fingerprint check failed, which leads to additional security checks.
+Such a strategy can be combined two-factor authentification.
+For example, in the event where the device used for receiving SMS is stolen, a fingerprint of the stolen device might reveal the unusual state of it as the fingerprint check failed, which leads to additional security checks.
 
-In general, the strategy can prevent or make the below attack more difficult: 
+In general, this strategy can prevent or make the below attacks more difficult: 
 \begin{itemize}
     \item \textbf{Naive Attack} A naive attack is defined as a conventional password-guessing attack that does not attempt to provide a matching fingerprint.
-Device fingerprint can effectively counter this attack since the attacker is assumed to launch the attack in a rather different environment.
-    \item \textbf{Optimized Password and Fingerprint Guessing}: The attacker might prepare a common profile of fingerprint and uses the popular profile of fingerprint to launch a naive attack by guess the passwords.
-Device fingerprint can effectively reduce the chance of success under this attack given that the fingeprint information expands the guessing space, and the attacker is only allowed with limited number of trials.
-    \item \textbf{Fingerprint Spoofing and Phishing}: Just like the normal password spoofing and phishing attack, the attacker can collect fingerprint information from users on top of the password.
-The level of spoofing resistence used in fingerprint will then largely determine the feasibility of this attack.
+A device fingerprint can effectively counter this attack since the attacker is assumed to launch the attack in a rather different environment.
+    \item \textbf{Optimized Password and Fingerprint Guessing}: The attacker might prepare common fingerprint profiles and use it along with to launch a naive password-guessing attack.
+A device fingerprint can effectively reduce the chances of success under this attack given that the fingeprint information expands the guessing space, and the attacker is only allowed a limited number of trials.
+    \item \textbf{Fingerprint Spoofing and Phishing}: Just like a normal password spoofing and phishing attack, the attacker can collect fingerprint information from users on top of the password.
+The level of spoofing resistence in the fingerprint used will then largely determine the feasibility of this attack.
 \end{itemize}
@@
 This could be strenghened by validating the fingerprint information at each request.
-If the set of fingerprints that the server collect is static, the recomputation of the fingerprint at each request is redundant.
+If the set of fingerprints that the server collects remains static, the recomputation of the fingerprint at each request is redundant.
 
@@
 The attacker can launch a XSS targeted at the victim, and steal the plaintext device fingerprint and the counter at the client-side.
-Once obtaining the fingerprint plaintext, the attacker can reproduce the hash by increment the counter
+Once obtaining the fingerprint plaintext, the attacker can reproduce the hash by incrementing the counter
 and recomputing.
-In addition, such XSS hijack attack is also possible even if the server dynamically changes the set of fignerprint in each request \cite{unger:shpf} as the attacker can simply collect additional information about the target device once hijack is sucessful.
+In addition, such an attack is also possible even if the server dynamically changes the set of fignerprint attributes in each request \cite{unger:shpf} as the attacker can simply collect additional information about the target device once the hijacking is successful.
 

### 2018-11-08 paper.tex
Add title
Fix typo in abstract

@@
 
-\title{Fingerprinting
+\title{Device fingerprinting for user authentication in web applications
 \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
     Device fingerprinting is a modern technique which, instead of using traditional user identifiers (e.g. cookies and local storage), leverages on existing information available from user's device.
-    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information.
+    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentication systems that utilize such fingerprint information.
 We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication.

### 2018-11-09 paper.tex
Add other author info
Remove extraneous spaces and fix typos

@@
 Ang Wei Ming\\
-       \email{trovato@corporation.com}
+       \email{e0177154@u.nus.edu}
 % 2nd. author
@@
 Chan Liang Fei Jeremy\\
-       \email{webmaster@marysville-ohio.com}
+       \email{e0053073@u.nus.edu}
 % 3rd. author
@@
 Ong Yong Siang\\
-       \email{larst@affiliation.org}
+       \email{e0032188@u.nus.edu}
 \and  % use '\and' if you need 'another row' of author names
@@
 \section{Introduction}
-- Background in terms of old cookie and local storaged based user identification techniques.
-- The motivation and driver for a new technology: Fingerprint
+\subsection{Background}
+Traditional password-based authentication systems require a user to provide two pieces of information: an identifer and a password proving their identity.
+The weaknesses of such a system largely hinge on the security of said password.
+For example, users may set weak passwords, allowing the security of their account to be comprimised as attackers use brute-force attacks to gain access.
+On the server side, the storage of these passwords or their representations also prove to be a problem, as they present themselves as valuable targets for attackers looking to comprimise a large number of users.
 
-- Intro of the technoloy, its history, and context.
+In this paper, we explore an alternative method to identifying and authenticating users using device fingerprinting.
+Device fingerprinting refers to techniques that collect information about the attributes and configuration of a device for the purpose of constructing a unique identifier for that device.
+Since this identifier is unique and can be generated without the intervention of the user, it can be used to build a passwordless authentication system where the user need only remember their username.
+The system will then compute a unique identifer for the device and check that with the one stored in its database, allowing the user access if the fingerprints match over a certain threshold.
+
+\subsection{What is device fingerprinting?}
+Device fingerprinting has its roots in its use by online analytics and advertising companies.
+In order to track a user across different websites, and to serve them relevant advertisements, these companies require a way to be able to identify the same device across different websites.
+The traditional method relies on placing a tracking cookie that contains a unique identifer on the device when it first visits a website that contains their analytics or advertising script.
+This would then allow the company to associate visits on different websites that they manage to the same user, and correlate data from those different visits knowing that they come from the same device.
+
+However, this traditional cookie based method presents a few problems, mainly in the form of persistence.
+Cookies are generally not guaranteed to last for any amount of time, since they can be cleared any time by the user.
+More recently, as privacy concerns over tracking has arisen, some browsers such as Safari have taken to blocking tracking cookies by default, making cookie based identifiers less reliable.
+
+Therefore, these companies have turned to device fingerprinting as a more effective method of device identification.
+By computing a unique identifier from the attributes of the device, advertisers can now store a identifier that would persist across users clearing their cookies, since recomputation of the identifier on the same device would yield the same hash.
+More importantly, device fingerprinting could generate identifiers that were consistent across different browsers on the same machine, or even across minor software and hardware changes.
+
+This enhanced persistence, as well as its use by advertsing and analytics companies for the purposes of tracking users, means that device fingerprinting is traditionally regarded as privacy invading, and as a technique that undermines security.
+However, the same properties that makes device fingerprinting attractive for tracking users also mean that it is a viable authentication method.
+Since it requires no input, it is far easier for a user to authenticate themselves through a device fingerprinting based authentication system.
+Moreover, since the fingerprint is tied to the inherent attributes of the device, it is difficult for an attacker to trivially attack and forge an identifier the same way they might brute force a password, since the interaction between the device fingerprint and the device itself may be hard to simulate.
+
+Therefore, we would like to explore the usage of device fingerprinting as a security enhancing technique, specifically in constructing a authentication system that is able to authenticate users with their unique device fingerprint, thus eliminating the need for passwords.
 
@@
 In order for this strategy to work, the server must be able to store persistently the fingerprint data which is given by the user at registration. 
-Such a strategy can be combined two-factor authentification.
+Such a strategy can be combined with two-factor authentication.
 For example, in the event where the device used for receiving SMS is stolen, a fingerprint of the stolen device might reveal the unusual state of it as the fingerprint check failed, which leads to additional security checks.

### 2018-11-09 paper.tex
Add extensions

@@
 
-\section{Extension}
-- What else can be done?
+\section{Extensions}
+\subsection{Improvements to be made}
+One of the issues regarding the current fingerprinting technology that we did not cover in depth is the comparison between accuracy and convenience of the technology.
+As mentioned previously in Section 3.3, in order to use fingerprinting technology as an authentication method, there needs to be stability across different scenarios.
+Minor changes made to a user's device such as a screen resolution change have to be handled either by accepting or rejecting the changes in the fingerprint.
+However, the only way that we can accept this change in our current implementation is by ignoring this specific set of data.
+This is because device fingerprinting results in a hash and any changes can cause the hash to be totally different.
+
+\paragraph{Accuracy vs Convenience}
+In order to increase the accuracy of fingerprinting technology, we have to include as many different data that can be acquired from the device as possible so as to get more unique values.
+This results in less convenience for the users as they have to fall back to a two factor authentication in order for the system to recompute their fingerprint.
+Further research will have to be conducted to find the set of data that is most optimized for both accuracy as well as convenience.
+Another method to improve the convenience without affecting too much of the accuracy is to use fuzzy hashing to compute the fingerprint hash as fuzzy hashing allows for small changes in the input without affecting the resulting hash.
+Therefore, it will then be able to handle changes that are small while still detecting large changes such as logging in from a completely different system.
 
 \section{Conclusion}
+In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique hashed fingerprints.
+
+By combining various components of a device's properties, we could increase the fingerprint entropy as well as obtain a hash unqiue for an individual's device, correspondingly unique to an individual.
+
+Although an device's fingerprint could change over time, we have considered that a user can be re-authenticated using a one-time password sent to their registered email.
+
+It is worth noting that fingerprinting alone however, cannot prevent attacks such as session hijacking where a perpetrator can simply collect additional information about the target device once the hijacking is successful.
+
+All in all, we think that fingerprinting is useful and provides a viable authentication method allowing users to be authenticated easily and such technology can be explored further in future security implementations.
 

### 2018-11-09 paper.tex

--- 2018-11-09 paper.tex
@@
 \section{Conclusion}
+In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique hashed fingerprints.
+
+By combining various components of a device's properties, we could increase the fingerprint entropy as well as obtain a hash unqiue for an individual's device, correspondingly unique to an individual.
+
+Although an device's fingerprint could change over time, we have considered that a user can be re-authenticated using a one-time password sent to their registered email.
+
+It is worth noting that fingerprinting alone however, cannot prevent attacks such as session hijacking where a perpetrator can simply collect additional information about the target device once the hijacking is successful.
+
+All in all, we think that fingerprinting is useful and provides a viable authentication method allowing users to be authenticated easily and such technology can be explored further in future security implementations.
 

### 2018-11-09 paper.tex
Added plugin

@@
 
-\section{Related work}
-- A survey of related work, what has been done, cite some papers and summarize
-
 \section{Fingerprint Technology}
@@
 \section{Fingerprint Auth Plugin}
-What we built
-\subsection{Design}
-What is the design of the system. 
-- Flow
-- Architecture. (I believe it will be easy)
+This section discusses the design and implementation of our device fingerprinting technique on a web application.
 
-\subsection{Implementation}
-- What are the modules, key functions, some hacky tricks
+The aim of our project is to showcase the possibility that a unique device fingerprint could potentially replace passwords in scenarios where a user needs to be authenticated.
+In our web application, users are allowed to sign up an account using only an email.
+During registration, our web application will generate a unique fingerprint hash that pairs with the email provided.
+Once registered, users can proceed to login using their registered email - they will be authenticated based on the pair of information containing both email and fingerprint hash.
+This single-field input provides simplicity and ease for users, eliminating the need to remember passwords howbeit without compromising security.
+
+\subsection{Device Fingerprint Plugin}
+The mechanism to generate a device fingerprint is the key and integral part of project.
+We built a plugin, consolidated into one single Javascript file that could analyze and collect a device’s information from a series of 27 components listed below.
+Each component is weighted according to its uniqueness across different devices.
+For instance, \textit{pixelRatio} is given a higher percentage than userAgent as it would vary more differently.
+The values and resulting percentages from each component is then combined into a hashed fingerprint unique for the device.
+
+%%% TODO List of attributes
+\begin{itemize}
+    \item userAgent: the User-Agent string of the browser eg. \verb|Mozilla/5.0| (\verb|Windows NT 10.0|; \verb|Win64|)
+    \item language: the current language used in the browser, eg. \verb|en-GB|
+    \item colourDepth:  the colour depth of the device in bits eg. $24$.
+      deviceMemory - the amount of memory on the device in gigabytes eg. $4$
+  \item pixelRatio - ratio of device pixels to CSS pixels eg. \verb|2|
+  \item hardwareConcurrency - number of logical processors eg. $8$
+  \item screenResolution - width and height of the current screen eg. $864,1536$
+  \item availableScreenResolution - width and height of the current screen available eg. $824,1536$
+  \item  timezoneOffset - offset from the GMT timezone in minutes eg. $-480$
+  \item timezone - current timezone eg. $Asia/Singapore$
+  \item sessionStorage - whether the HTML5 session storage API is available eg. $true$
+  \item localStorage - whether the HTML5 localStorage API is available eg. $true$
+  \item indexedDb - whether the HTML5 indexedD API is available eg. $true$
+  \item addBehavior - whether addBehaviour is available eg. $false$
+  \item openDatabase - whether WebSQL is available eg. $true$
+  \item cpuClass - CPU class of the device eg. \verb|Win32|
+  \item platform - platform of the device eg. \verb|Win32|
+  \item doNotTrack - whether the Do Not Track setting is on eg. $false$
+  \item plugins - list of plugins installed
+  \item canvas - canvas fingerprint of browser
+  \item webgl - WebGL fingerprint of browser
+  \item webglVendorAndRenderer - WebGL vendor and renderer of browser
+  \item adBlock - whether the browser has an ad blocker installed eg. $false$
+  \item touchSupport - whether the device has a touchscreen interface, with no. of touchpoints eg. $10, false,false$
+  \item fonts - detection of all user installed fonts
+  \item audio - audio fingerprint of device
+\end{itemize}
+
+The idea of a single-file Javascript plugin considers scalability whereby it could be imported into any web application for the purpose of generating a device’s fingerprint.
+
+\subsection{Demo Web Application}
+The plugin above has been fitted into our streamlined web application to exemplify the fingerprint-based authentication.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/demo-flow.png}
+    \caption{Demo Flow of Web Application}
+    \label{fig:demo-flow}
+\end{figure}
+
+As shown in Figure \ref{fig:demo-flow}, our web application consists of three components - User Interface (UI), Server and a Database.
+
+The front-end user interface that displays the registration and login page is built with Angular 6.0, designed with Material Design Bootstrap for aesthetics.
+The UI is in charged of calling the function of our fingerprint plugin to generate a device fingerprint and thereby package both user input email and hashed fingerprint into a JSON object, passing it to the NodeJS server.
+
+The NodeJS server utilizes Express 4.0 API routing for communication of data between front-end and database.
+For storing and retrieving of data, it uses Flex.Query Processor Library to execute SQL statements to a MySQL instance.
+
+\begin{itemize}
+    \item \textbf{Sign Up Flow:}
+        \begin{enumerate}
+        \item User signs up with an email  
+        \item UI generates fignerprint hash  
+        \item UI sends fingerprint hash and email of the registering user to backend  
+        \item UI displays the fingerprint hash to user  
+        \item Backend stores fingerprint hash and email into the database  
+        \end{enumerate}
+
+    \item \textbf{Login Flow:}
+        \begin{enumerate}
+        \item User logs in with email  
+        \item UI generates fingerprint hash  
+        \item UI sends fingerprint hash and email to backend  
+        \item Backend checks whether there exists any record for the pair of information and returns either true or false to authenticate the user  
+        \item UI prompts login success / failure  
+\end{enumerate}
+\end{itemize}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/ui.png}
+    \caption{UI for the Web Applicaiton}
+    \label{fig:ui}
+\end{figure}
 

### 2018-11-09 paper.tex

@@
 
-\section{Extension}
-- What else can be done?
+\section{Extensions}
+\subsection{Improvements to be made}
+One of the issues regarding the current fingerprinting technology that we did not cover in depth is the comparison between accuracy and convenience of the technology.
+As mentioned previously in Section 3.3, in order to use fingerprinting technology as an authentication method, there needs to be stability across different scenarios.
+Minor changes made to a user's device such as a screen resolution change have to be handled either by accepting or rejecting the changes in the fingerprint.
+However, the only way that we can accept this change in our current implementation is by ignoring this specific set of data.
+This is because device fingerprinting results in a hash and any changes can cause the hash to be totally different.
+
+\paragraph{Accuracy vs Convenience}
+In order to increase the accuracy of fingerprinting technology, we have to include as many different data that can be acquired from the device as possible so as to get more unique values.
+This results in less convenience for the users as they have to fall back to a two factor authentication in order for the system to recompute their fingerprint.
+Further research will have to be conducted to find the set of data that is most optimized for both accuracy as well as convenience.
+Another method to improve the convenience without affecting too much of the accuracy is to use fuzzy hashing to compute the fingerprint hash as fuzzy hashing allows for small changes in the input without affecting the resulting hash.
+Therefore, it will then be able to handle changes that are small while still detecting large changes such as logging in from a completely different system.
 

### 2018-11-15 paper.tex
Update extensions based on current implementation

--- 2018-11-09 paper.tex
@@
 
-\section{Extension}
-- What else can be done?
+\section{Extensions}
+
+\subsection{Improvements to be made}
+
+In our current implementation, we allow for variations in the components of a fingerprint by assigning a weightage to each component that determines the unlikelihood of the value changing.
+These weightages are used during the authentication stage to calculate the amount of variations the current fingerprint has compared to the original fingerprint stored in the database.
+However, in order to support such variations, there are few other issues that we have to consider.
+
+\paragraph{Accuracy or Convenience}
+The tradeoff between the accuracy and convenience is one such issue that we did not cover in detail.
+Even though our implementation includes various security levels, we did not investigate the optimal threshold level that should be set for the different levels of security or the optimal algorithm to calculate the amount of variation for each component.
+
+Increasing the threshold for the amount of variations will increase the accuracy of this authentication while at the same time provide inconvenience to the users since they are unable to make any changes to their device configurations.
+On the other hand, if the threshold is lowered, though the authenticity of the users might be affected, users are instead able to log in successfully even though they have installed a new font or changed their screen resolution after they registered their fingerprints.
+To aid with the optimal threshold level, custom algorithms for check each component can also be implemented.
+For instance, a change in the language component from en-US (English - United States) to en-SG (English - Singapore) can have a lower amount of variation compared to a change from en-US to ru-RU (Russian - Russia).
+Further studies will have to be conducted to find the optimal threshold level, the weightage for each components as well as the algorithm to check each component.
+
+Another concern regarding accuracy and convenience is that there is no security level that is able to fit different use cases.
+For a certain use case, using a medium security level will be sufficient while for another specific use case, we may have to use a low security level.
+One method to go about solving this issue is to allow for more detailed customization by the users themselves.
+For example, if a certain user travels frequently due to work, the user will have the value of the timezone component change regularly.
+In this case, it is better to reduce the effect the timezone component has on the amount of variations.
+Therefore, the timezone component can adjusted a lower weightage just for this specific user.
+
+\paragraph{Changing of Hardware Configurations}
+Though most devices connected to the internet are mobile devices such as smartphones, tablets and laptops, where the hardware are unlikely to change, there are still a significant number of desktop computers being used.
+The hardware of desktop computers can change over time since users will likely upgrade their computer's components when it gets outdated.
+This can reduce the success rate of fingerprint authentication and will require the users to reregister their fingerprint when the new device fingerprint differs too much from the original.
+Instead of updating the fingerprint everytime a variation is detected, a proposed solution is to normalize the device fingerprint over time.
+This allows for the device to go through different configurations over a period of time while still maintaining both the accuracy and convenience.
+It is also able to handle the use case mentioned previously where a the timezone component can also change over time when a user is travelling over multiple countries.
+
+\paragraph{Multi-device Support}
+Adding multi-device support to our current implementation is as easy as registering multiple device fingerprints for each user account.
+However, though this is possible, supporting multiple devices for a single user comes with its own limitations, which is scalabilty.
+Having multiple fingerprints for one user means that when logging into the account, the server checks the current device fingerprint with the list of fingerprints registered under that specific user.
+As the size of the fingerprint is larger than usual passwords and each components have to be checked with its own algorithm, a user with a significant number of devices will take a much longer time to authenticate.
+Further more, because our implementation allows variations in the device fingerprints, we will be unable to tell which fingerprints stored on the server is the current fingerprint's variation.
+This prevents us from using the method where we normalize a fingerprint over time.
+
+\subsection{Real World Implementation}
+Before we start using fingerprint authentication in a real world application, it is very important to ensure that a 2FA (Two Factor Authentication) is in place.
+This is because in the event where a user's device fingerprint changes significantly more than the allowed threshold, we are still able to use the 2FA to authenticate the user, and at the same time reregister the user's device fingerprint into the database.
 

### 2018-11-15 paper.tex
Update extensions based on current implementation (#5)
* Update extensions based on current implementation

* Made some phrasing changes

--- 2018-11-09 paper.tex
@@
 
-\section{Extension}
-- What else can be done?
+\section{Extensions}
+
+\subsection{Improvements to be made}
+
+In our current implementation, we allow for variations in the components of a fingerprint by assigning a weight to each component that represents the unlikelihood of the value changing.
+These weights are used during the authentication stage to calculate how different the current fingerprint is compared to the original fingerprint stored in the database.
+However, in order to support such variations, there are few other issues that we have to consider.
+
+\paragraph{Accuracy or Convenience}
+The tradeoff between accuracy and convenience is one such issue that we did not cover in detail.
+Even though our implementation includes various security levels, we did not investigate the optimal threshold level that should be set for the different levels of security or the optimal algorithm to calculate the amount of variation for each component.
+
+Increasing the threshold for the amount of variation will increase the accuracy of  authentication while at the same time provide inconvenience to the users since they are unable to make any changes to their device configuration.
+On the other hand, if the threshold is lowered, though the authenticity of the users might be affected, users are instead able to log in successfully even though they have installed a new font or changed their screen resolution after they registered their fingerprints.
+To aid with the optimal threshold level, custom algorithms for check each component can also be implemented.
+For instance, a change in the language component from en-US (English - United States) to en-SG (English - Singapore) can have a lower amount of variation compared to a change from en-US to ru-RU (Russian - Russia).
+Further studies will have to be conducted to find the optimal threshold level, the weights for each component as well as the algorithm to check each component.
+
+Another concern regarding accuracy and convenience is that there is no one security level that is able to fit different use cases.
+For a certain use case, using a medium security level may be sufficient while for another specific use case, we may have to use a low security level.
+One method to go about solving this issue is to allow for more detailed customization by the users themselves.
+For example, if a certain user travels frequently due to work, the user will have the value of the timezone component change regularly.
+In this case, it is better to reduce the effect the timezone component has on the amount of variations.
+Therefore, the timezone component can adjusted a lower weight just for this specific user.
+
+\paragraph{Change of Hardware Configurations}
+Though most devices connected to the internet are mobile devices such as smartphones, tablets and laptops, where the hardware are unlikely to change, there are still a significant number of desktop computers being used.
+The hardware of desktop computers can change over time since users will likely upgrade their computer's components as they get outdated.
+This can reduce the success rate of fingerprint authentication and will require the users to re-register their fingerprint when the new device fingerprint differs too much from the original.
+Instead of updating the fingerprint every time a variation is detected, a proposed solution is to normalize the device fingerprint over time.
+This allows for the device to go through different configurations over a period of time while still maintaining both the accuracy and convenience.
+It is also able to handle the use case mentioned previously where a the timezone component can also change over time when a user is travelling over multiple countries.
+
+\paragraph{Multi-device Support}
+Adding multi-device support to our current implementation is as easy as registering multiple device fingerprints for each user account.
+However, though this is possible, supporting multiple devices for a single user comes with its own limitations such as scalabilty.
+Having multiple fingerprints for one user means that when logging into the account, the server would need to check the current device fingerprint with the list of fingerprints registered under that specific user.
+As the size of the fingerprint is larger than regular passwords and each components have to be checked with its own algorithm, a user with a significant number of devices will take a much longer time to authenticate.
+Further more, because our implementation allows for  variations in the device fingerprints, we will be unable to tell which fingerprints stored on the server is the current fingerprint's variation.
+This prevents us from using the method where we normalize a fingerprint over time.
+
+\subsection{Real World Implementation}
+Before we start using fingerprint authentication in a real world application, it is very important to ensure that a 2FA (Two Factor Authentication) is in place.
+This is because in the event where a user's device fingerprint changes significantly more than the allowed threshold, we are still able to use 2FA to authenticate the user, and at the same time reregister the user's device fingerprint into the database.
 

### 2018-11-15 paper.tex
Added fingerprint as sole auth method discussion

--- 2018-11-09 paper.tex
@@
     In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentication systems that utilize such fingerprint information.
-We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication.
+We analyzes the trade-off between the uniqueness of the identifier generated and ease of use for authentication.
 Lastly, we also build a simple authentication system that can be reused and extended in real-world web applications.
@@
 \subsection{Background}
-Traditional password-based authentication systems require a user to provide two pieces of information: an identifer and a password proving their identity.
+Traditional password-based authentication systems require a user to provide two pieces of information: an identifier and a password proving their identity.
 The weaknesses of such a system largely hinge on the security of said password.
-For example, users may set weak passwords, allowing the security of their account to be comprimised as attackers use brute-force attacks to gain access.
-On the server side, the storage of these passwords or their representations also prove to be a problem, as they present themselves as valuable targets for attackers looking to comprimise a large number of users.
+For example, users may set weak passwords, allowing the security of their account to be compromised as attackers use brute-force attacks to gain access.
+On the server side, the storage of these passwords or their representations also prove to be a problem, as they
+present themselves as valuable targets for attackers looking to compromise a large number of users.
 
@@
 Device fingerprinting refers to techniques that collect information about the attributes and configuration of a device for the purpose of constructing a unique identifier for that device.
-Since this identifier is unique and can be generated without the intervention of the user, it can be used to build a passwordless authentication system where the user need only remember their username.
-The system will then compute a unique identifer for the device and check that with the one stored in its database, allowing the user access if the fingerprints match over a certain threshold.
+Since this identifier is unique and can be generated without the intervention of the user, it can be used to build a password-less authentication system where the user need only remember their
+username.
+The system will then compute a unique identifier for the device and check that with the one stored in its database, allowing the user access if the fingerprints match over a certain threshold.
 
@@
 In order to track a user across different websites, and to serve them relevant advertisements, these companies require a way to be able to identify the same device across different websites.
-The traditional method relies on placing a tracking cookie that contains a unique identifer on the device when it first visits a website that contains their analytics or advertising script.
+The traditional method relies on placing a tracking cookie that contains a unique identifier on the device when it first visits a website that contains their analytics or advertising script.
 This would then allow the company to associate visits on different websites that they manage to the same user, and correlate data from those different visits knowing that they come from the same device.
@@
 Therefore, these companies have turned to device fingerprinting as a more effective method of device identification.
-By computing a unique identifier from the attributes of the device, advertisers can now store a identifier that would persist across users clearing their cookies, since recomputation of the identifier on the same device would yield the same hash.
+By computing a unique identifier from the attributes of the device, advertisers can now store a identifier that would persist across users clearing their cookies, since re-computation of the identifier on the same device would yield the same hash.
 More importantly, device fingerprinting could generate identifiers that were consistent across different browsers on the same machine, or even across minor software and hardware changes.
 
-This enhanced persistence, as well as its use by advertsing and analytics companies for the purposes of tracking users, means that device fingerprinting is traditionally regarded as privacy invading, and as a technique that undermines security.
+This enhanced persistence, as well as its use by advertising and analytics companies for the purposes of tracking users, means that device fingerprinting is traditionally regarded as privacy invading, and as a technique that undermines security.
 However, the same properties that makes device fingerprinting attractive for tracking users also mean that it is a viable authentication method.
@@
 
-With the amount of information given away from the browser, they can be identified in a stable and mesurable manner \cite{niki:cookie} by embedding scripts that collect and process those information into the web page, as shown by Nikiforaskis.
+With the amount of information given away from the browser, they can be identified in a stable and measurable manner \cite{niki:cookie} by embedding scripts that collect and process those information into the web page, as shown by Nikiforaskis.
 Eckersley from the Panopticlick project \cite{panop} demonstrates that browser fingerprinting technology is a fairly effective user tracking tool, drawing attention and usage from many advertising companies.
@@
 Take one of the extensions that expose additional
-information as an example: \verb|NoScript| \cite{noscript}, which is an extension that blocks executions of Web objects from any URL but those whitelisted.
+information as an example: \verb|NoScript| \cite{noscript}, which is an extension that blocks executions of Web objects from any URL but those white-listed.
 As explained by Mowery et al.
-\cite{mowery:fg}, one can prepare a list of URLs in the web page and see which of them are listed on the whitelist.
-The whitelist of the extension then can be used as an identifier to differentiate users from each other.
+\cite{mowery:fg}, one can prepare a list of URLs in the web page and see which of them are listed on the white-list.
+The white-list of the extension then can be used as an identifier to differentiate users from each other.
 
@@
 \cite{pierre:beauty} demonstrates that one can combine at least 17 attributes from various sources to create unique device fingerprints.
-As shown in Figure \ref{fig:amiunique}, the possible number of combinations of the different vlaues from those parameters is rather large, and the study successfully identified $81\%$ users out of 118,000 users.
+As shown in Figure \ref{fig:amiunique}, the possible number of combinations of the different values from those parameters is rather large, and the study successfully identified $81\%$ users out of 118,000 users.
 
@@
 A set of inappropriate fingerprinting practices may incur too many false negatives in the authentication process, denying legitimate users access or falling back to the most conservative authentication process too frequently.
-Compared to the general usage of fingeprinting in advertising, fingerprinting for authentication requires a higher level of accuracy in distinguishing users.
+Compared to the general usage of fingerprint in advertising, fingerprinting for authentication requires a higher level of accuracy in distinguishing users.
 A $80\%$ or $90\%$ accuracy is simply not enough.
@@
 
-\paragraph{Stablility across different scenarios}
+\paragraph{Stability across different scenarios}
 It is normal for a user to have their device fingerprint change over time or in different scenarios. For example,  a user may be traveling across different time zones or switch between devices. 
 A significant change in the device fingerprints will usually lead to a fallback on a less convenient but reliable authentication process, such as a one-time code sent to the user's phone or email.
-Therefore, using fingerprint practices that are reliable over time for a particular user is prefereable.
+Therefore, using fingerprint practices that are reliable over time for a particular user is preferred.
 Having more diverse metrics collected from different fingerprint practices will allow a small subset of values to vary without decreasing the overall stability of the fingerprint.
@@
 It is related to but different from the stability requirement, which is primarily concerned  with changes in the device configuration.
-For some  fingerprinting techniques, such as measuring the JavaScript rendering performance (determined and related to the underlying GPU/CPU performance and load at a specific instance), the same device may generate different results with other applications running: for example, trying to login when having a video compliation job running in the background might produce different fingerprints.
+For some  fingerprinting techniques, such as measuring the JavaScript rendering performance (determined and related to the underlying GPU/CPU performance and load at a specific instance), the same device may generate different results with other applications running: for example, trying to login when having a video compilation job running in the background might produce different fingerprints.
 
-\paragraph {Resistence to spoofing}
+\paragraph {Resistance to spoofing}
 An attacker can potentially spoof a device fingerprint by mimicking the properties or behaviour of the targeted device.
@@
 For example, if the server relies on running a particular JavaScript script at the client side and retrieving the result from the client, then an attack can potentially replay the results to pretend to be the victim.
-On the other hand, some fingerprint technique are more resistent to such spoofing, such as the IP address of the sources\cite{beverly:ip} or timestamps indicating clock skew from MAC protocol packets \cite{ara:wire}.
+On the other hand, some fingerprint technique are more resistant to such spoofing, such as the IP address of the sources\cite{beverly:ip} or timestamps indicating clock skew from MAC protocol packets \cite{ara:wire}.
 
@@
 \subsubsection{Fingerprint Authentication Solution}
-In this section, we discuss two strategies of using fingerprinting to augment authentication: (1) fingerprinting at session initialization, (2) fingerprinting throughout an authenticated session.
+In this section, we discuss two strategies of using fingerprinting to augment authentication: (1) fingerprinting at session initialization, (2) fingerprinting throughout an authenticated session, (3) fingerprinting as the primary authentication method.
 
@@
     \item \textbf{Optimized Password and Fingerprint Guessing}: The attacker might prepare common fingerprint profiles and use it along with to launch a naive password-guessing attack.
-A device fingerprint can effectively reduce the chances of success under this attack given that the fingeprint information expands the guessing space, and the attacker is only allowed a limited number of trials.
+A device fingerprint can effectively reduce the chances of success under this attack given that the fingerprint information expands the guessing space, and the attacker is only allowed a limited number of trials.
     \item \textbf{Fingerprint Spoofing and Phishing}: Just like a normal password spoofing and phishing attack, the attacker can collect fingerprint information from users on top of the password.
-The level of spoofing resistence in the fingerprint used will then largely determine the feasibility of this attack.
+The level of spoofing resistance in the fingerprint used will then largely determine the feasibility of this attack.
 \end{itemize}
@@
 In a typical password-based web authentication scheme, the server will return a cookie upon receiving a valid username and password so that the client will use the cookie as a proof of authentication in every request later on.
-This could be strenghened by validating the fingerprint information at each request.
-If the set of fingerprints that the server collects remains static, the recomputation of the fingerprint at each request is redundant.
+This could be strengthened by validating the fingerprint information at each request.
+If the set of fingerprints that the server collects remains static, the re-computation of the fingerprint at each request is redundant.
 
-A simple replay attack can be effecively prevented by hashing the fingerprint at the client with a counter before sending to the server, as demonstrated by \cite{preu:smart}.
+A simple replay attack can be effectively prevented by hashing the fingerprint at the client with a counter before sending to the server, as demonstrated by \cite{preu:smart}.
 However, for a more powerful attack such as XSS attack, it is less effective.
-The attacker can launch a XSS targeted at the victim, and steal the plaintext device fingerprint and the counter at the client-side.
-Once obtaining the fingerprint plaintext, the attacker can reproduce the hash by incrementing the counter
+The attacker can launch a XSS targeted at the victim, and steal the plain-text device fingerprint and the counter at the client-side.
+Once obtaining the fingerprint plain-text, the attacker can reproduce the hash by incrementing the counter
 and recomputing.
-In addition, such an attack is also possible even if the server dynamically changes the set of fignerprint attributes in each request \cite{unger:shpf} as the attacker can simply collect additional information about the target device once the hijacking is successful.
+In addition, such an attack is also possible even if the server dynamically changes the set of fingerprint attributes in each request \cite{unger:shpf} as the attacker can simply collect additional information about the target device once the hijacking is successful.
+
+\paragraph{ Fingerprint as the primary authentication method}
+The previous two approaches focus on how fingerprint can easily extend the current web authentication methods.
+We now present an approach where fingerprinting is used as the main authentication method, with supports from 2FA (like email, or SMS).
+Using fingerprint as the main authentication method requires a few assumptions to be held true: 
+\begin{itemize}
+    \item Each device should have a unique fingerprint that can be associated with a user's account.
+From the previous sections results, while this is still not entirely true, it is believed that the potential huge number of attributes from a device fingerprint should set apart each user as more features can be collected from a device with more powerful fingerprinting methods.
+    \item Fingerprints collected from the same device at different occasions need to be relatively stable, and there needs to be ways to re-associate a device to the account: recovery mechanism such as email or SMS can be viable options.
+    \item Even though an attacker has full knowledge of the device's hardware and software information, the attacker should not be able to spoof the device if she/he does not have access to the device.
+\end{itemize}
+
+If the above requirements can be met, device fingerprinting alone could be used in real life for account authentication.
+In the below sections, we will present a prototype that demonstrates the usage of fingerprint-based authentication method, and also discuss limitations that are closely related to the above requirements, and possible solutions to address them.
 

### 2018-11-16 paper.tex
Added fingerprint as sole auth method discussion (#6)

@@
 \section{Extensions}
+
 \subsection{Improvements to be made}
-One of the issues regarding the current fingerprinting technology that we did not cover in depth is the comparison between accuracy and convenience of the technology.
-As mentioned previously in Section 3.3, in order to use fingerprinting technology as an authentication method, there needs to be stability across different scenarios.
-Minor changes made to a user's device such as a screen resolution change have to be handled either by accepting or rejecting the changes in the fingerprint.
-However, the only way that we can accept this change in our current implementation is by ignoring this specific set of data.
-This is because device fingerprinting results in a hash and any changes can cause the hash to be totally different.
 
-\paragraph{Accuracy vs Convenience}
-In order to increase the accuracy of fingerprinting technology, we have to include as many different data that can be acquired from the device as possible so as to get more unique values.
-This results in less convenience for the users as they have to fall back to a two factor authentication in order for the system to recompute their fingerprint.
-Further research will have to be conducted to find the set of data that is most optimized for both accuracy as well as convenience.
-Another method to improve the convenience without affecting too much of the accuracy is to use fuzzy hashing to compute the fingerprint hash as fuzzy hashing allows for small changes in the input without affecting the resulting hash.
-Therefore, it will then be able to handle changes that are small while still detecting large changes such as logging in from a completely different system.
+In our current implementation, we allow for variations in the components of a fingerprint by assigning a weight to each component that represents the unlikelihood of the value changing.
+These weights are used during the authentication stage to calculate how different the current fingerprint is compared to the original fingerprint stored in the database.
+However, in order to support such variations, there are few other issues that we have to consider.
+
+\paragraph{Accuracy or Convenience}
+The tradeoff between accuracy and convenience is one such issue that we did not cover in detail.
+Even though our implementation includes various security levels, we did not investigate the optimal threshold level that should be set for the different levels of security or the optimal algorithm to calculate the amount of variation for each component.
+
+Increasing the threshold for the amount of variation will increase the accuracy of  authentication while at the same time provide inconvenience to the users since they are unable to make any changes to their device configuration.
+On the other hand, if the threshold is lowered, though the authenticity of the users might be affected, users are instead able to log in successfully even though they have installed a new font or changed their screen resolution after they registered their fingerprints.
+To aid with the optimal threshold level, custom algorithms for check each component can also be implemented.
+For instance, a change in the language component from en-US (English - United States) to en-SG (English - Singapore) can have a lower amount of variation compared to a change from en-US to ru-RU (Russian - Russia).
+Further studies will have to be conducted to find the optimal threshold level, the weights for each component as well as the algorithm to check each component.
+
+Another concern regarding accuracy and convenience is that there is no one security level that is able to fit different use cases.
+For a certain use case, using a medium security level may be sufficient while for another specific use case, we may have to use a low security level.
+One method to go about solving this issue is to allow for more detailed customization by the users themselves.
+For example, if a certain user travels frequently due to work, the user will have the value of the timezone component change regularly.
+In this case, it is better to reduce the effect the timezone component has on the amount of variations.
+Therefore, the timezone component can adjusted a lower weight just for this specific user.
+
+\paragraph{Change of Hardware Configurations}
+Though most devices connected to the internet are mobile devices such as smartphones, tablets and laptops, where the hardware are unlikely to change, there are still a significant number of desktop computers being used.
+The hardware of desktop computers can change over time since users will likely upgrade their computer's components as they get outdated.
+This can reduce the success rate of fingerprint authentication and will require the users to re-register their fingerprint when the new device fingerprint differs too much from the original.
+Instead of updating the fingerprint every time a variation is detected, a proposed solution is to normalize the device fingerprint over time.
+This allows for the device to go through different configurations over a period of time while still maintaining both the accuracy and convenience.
+It is also able to handle the use case mentioned previously where a the timezone component can also change over time when a user is travelling over multiple countries.
+
+\paragraph{Multi-device Support}
+Adding multi-device support to our current implementation is as easy as registering multiple device fingerprints for each user account.
+However, though this is possible, supporting multiple devices for a single user comes with its own limitations such as scalabilty.
+Having multiple fingerprints for one user means that when logging into the account, the server would need to check the current device fingerprint with the list of fingerprints registered under that specific user.
+As the size of the fingerprint is larger than regular passwords and each components have to be checked with its own algorithm, a user with a significant number of devices will take a much longer time to authenticate.
+Further more, because our implementation allows for  variations in the device fingerprints, we will be unable to tell which fingerprints stored on the server is the current fingerprint's variation.
+This prevents us from using the method where we normalize a fingerprint over time.
+
+\subsection{Real World Implementation}
+Before we start using fingerprint authentication in a real world application, it is very important to ensure that a 2FA (Two Factor Authentication) is in place.
+This is because in the event where a user's device fingerprint changes significantly more than the allowed threshold, we are still able to use 2FA to authenticate the user, and at the same time reregister the user's device fingerprint into the database.
 

### 2018-11-16 paper.tex
Integreated Keith's

@@
 
-The aim of our project is to showcase the possibility that a unique device fingerprint could potentially replace passwords in scenarios where a user needs to be authenticated.
-In our web application, users are allowed to sign up an account using only an email.
-During registration, our web application will generate a unique fingerprint hash that pairs with the email provided.
-Once registered, users can proceed to login using their registered email - they will be authenticated based on the pair of information containing both email and fingerprint hash.
-This single-field input provides simplicity and ease for users, eliminating the need to remember passwords howbeit without compromising security.
+The aim of our project is to showcase the possibility that a unique device fingerprint could potentially replace passwords in an authentication system.
+We built a web application where users can sign up and login to an account simply using an email.
+During registration, our web application will generate a unique device fingerprint that pairs with the email provided.
+Once registered, users can proceed to login using their registered email.
+During log-in, the application will also generate a log-in device fingerprint and the user will be authenticated based on the existence of email and the similarity between the log-in fingerprint and the registered fingerprint if the email provided exists.
+This single-field input authentication provides simplicity and ease for users, eliminating the need to remember passwords without compromising security.
 
-\subsection{Device Fingerprint Plugin}
-The mechanism to generate a device fingerprint is the key and integral part of project.
+The authentication algorithm introduces a degree of complexity whereby the similarity of two device fingerprints is evaluated based on a threshold level.
+This threshold level is customizable during registration (Figure \ref{fig:level}) and explained in the table below.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/level.png}
+    \caption{Security Levels For Demonstration}
+    \label{fig:level}
+\end{figure}
+
+The algorithm sets up for authentication by assigning a weightage to each component that make up the original fingerprint. This accounts for variations in a device fingerprint.
+
+In the current implementation, an email account is tied to one device fingerprint.
+In other words, the user can only use the device he/she registered the account with.
+This would be ideal in scenarios where a firm wishes to lock-down usage of an account strictly to a machine for tightened security purposes.
+However, this would not be ideal on platforms where user should be able to be authenticated across different devices.
+Hence, we have considered various measures such as using two-factor authentication by sending a one-time key to the registered email when logged in on an unidentified device (also elaborated in Extensions section) for future releases.
+
+\subsection{Device Fingerprint Generation}
+The mechanism to generate a device fingerprint is the key and integral part of our project.
 We built a plugin, consolidated into one single Javascript file that could analyze and collect a device’s information from a series of 27 components listed below.
+Some components are easy to get as they are avialble in JavaScript, while some are more invovled.
+For example, fingerprint for WebGL and Canvas required test rendering of objects dynamically to obtain the specific information.
 Each component is weighted according to its uniqueness across different devices.
-For instance, \textit{pixelRatio} is given a higher percentage than userAgent as it would vary more differently.
-The values and resulting percentages from each component is then combined into a hashed fingerprint unique for the device.
+For instance, pixelRatio is given a higher percentage than userAgent as it would vary more differently.
+The generated array of values and its weighted percentages are sent as a JSON object to be stored in the database.
 
@@
 \begin{itemize}
-    \item userAgent: the User-Agent string of the browser eg. \verb|Mozilla/5.0| (\verb|Windows NT 10.0|; \verb|Win64|)
-    \item language: the current language used in the browser, eg. \verb|en-GB|
-    \item colourDepth:  the colour depth of the device in bits eg. $24$.
-      deviceMemory - the amount of memory on the device in gigabytes eg. $4$
-  \item pixelRatio - ratio of device pixels to CSS pixels eg. \verb|2|
-  \item hardwareConcurrency - number of logical processors eg. $8$
-  \item screenResolution - width and height of the current screen eg. $864,1536$
-  \item availableScreenResolution - width and height of the current screen available eg. $824,1536$
-  \item  timezoneOffset - offset from the GMT timezone in minutes eg. $-480$
-  \item timezone - current timezone eg. $Asia/Singapore$
-  \item sessionStorage - whether the HTML5 session storage API is available eg. $true$
-  \item localStorage - whether the HTML5 localStorage API is available eg. $true$
-  \item indexedDb - whether the HTML5 indexedD API is available eg. $true$
-  \item addBehavior - whether addBehaviour is available eg. $false$
-  \item openDatabase - whether WebSQL is available eg. $true$
-  \item cpuClass - CPU class of the device eg. \verb|Win32|
-  \item platform - platform of the device eg. \verb|Win32|
-  \item doNotTrack - whether the Do Not Track setting is on eg. $false$
-  \item plugins - list of plugins installed
-  \item canvas - canvas fingerprint of browser
-  \item webgl - WebGL fingerprint of browser
-  \item webglVendorAndRenderer - WebGL vendor and renderer of browser
-  \item adBlock - whether the browser has an ad blocker installed eg. $false$
-  \item touchSupport - whether the device has a touchscreen interface, with no. of touchpoints eg. $10, false,false$
-  \item fonts - detection of all user installed fonts
-  \item audio - audio fingerprint of device
+    \item \textbf{userAgent}: the User-Agent string of the browser eg. \verb|Mozilla/5.0| (\verb|Windows NT 10.0|; \verb|Win64|)
+    \item \textbf{language}: the current language used in the browser, eg. \verb|en-GB|
+    \item \textbf{colourDepth}:  the colour depth of the device in bits eg. $24$.
+    \item\textbf{ deviceMemory} - the amount of memory on the device in gigabytes eg. $4$
+    \item\textbf{ pixelRatio} - ratio of device pixels to CSS pixels eg. \verb|2|
+    \item\textbf{ hardwareConcurrency} - number of logical processors eg. $8$
+    \item\textbf{ screenResolution} - width and height of the current screen eg. $864,1536$
+    \item\textbf{ availableScreenResolution} - width and height of the current screen available eg. $824,1536$
+    \item\textbf{  timezoneOffset} - offset from the GMT timezone in minutes eg. $-480$
+    \item\textbf{ timezone} - current timezone eg. $Asia/Singapore$
+    \item\textbf{ sessionStorage} - whether the HTML5 session storage API is available eg. $true$
+    \item\textbf{ localStorage} - whether the HTML5 localStorage API is available eg. $true$
+    \item\textbf{ indexedDb} - whether the HTML5 indexedD API is available eg. $true$
+    \item\textbf{ addBehavior} - whether addBehaviour is available eg. $false$
+    \item\textbf{ openDatabase} - whether WebSQL is available eg. $true$
+    \item\textbf{ cpuClass} - CPU class of the device eg. \verb|Win32|
+    \item\textbf{ platform} - platform of the device eg. \verb|Win32|
+    \item\textbf{ doNotTrack} - whether the Do Not Track setting is on eg. $false$
+    \item\textbf{ plugins} - list of plugins installed
+    \item\textbf{ canvas} - canvas fingerprint of browser
+    \item\textbf{ webgl} - WebGL fingerprint of browser
+    \item\textbf{ webglVendorAndRenderer} - WebGL vendor and renderer of browser
+    \item\textbf{ adBlock} - whether the browser has an ad blocker installed eg. $false$
+    \item\textbf{ touchSupport} - whether the device has a touchscreen interface, with no. of touchpoints eg. $10, false,false$
+    \item\textbf{ fonts} - detection of all user installed fonts
+    \item\textbf{ audio} - audio fingerprint of device
+    \item\textbf{ enumerateDevice} -  list of all media input and output devices, such as microphones or webcams
+
 \end{itemize}
@@
 \subsection{Demo Web Application}
-The plugin above has been fitted into our streamlined web application to exemplify the fingerprint-based authentication.
+The Javascript plugin above for generating device fingerprint was fitted into our streamlined web application to exemplify the fingerprint-based authentication.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{assets/demo-flow.png}
+    \includegraphics[width=0.5\textwidth]{assets/fig3-demo-flow.png}
     \caption{Demo Flow of Web Application}
@@
 
-The front-end user interface that displays the registration and login page is built with Angular 6.0, designed with Material Design Bootstrap for aesthetics.
-The UI is in charged of calling the function of our fingerprint plugin to generate a device fingerprint and thereby package both user input email and hashed fingerprint into a JSON object, passing it to the NodeJS server.
+The front-end user interface that displays the registration and login pages was built with Angular 6.0, designed with Material Design Bootstrap for a consistent and fluent design.
+Background animation was added to create an aesthetic appeal that blends into the “security” theme.
+The UI is responsible for input validations, sending and receiving data to-and-from the backend (NodeJS) server.
+It triggers the Javascript function of our fingerprint plugin to generate a device fingerprint and thereby package both user input email and device fingerprint into a JSON object, passing it to the NodeJS server.
 
-The NodeJS server utilizes Express 4.0 API routing for communication of data between front-end and database.
-For storing and retrieving of data, it uses Flex.Query Processor Library to execute SQL statements to a MySQL instance.
+The NodeJS server utilizes Express 4.0 for communication of data between front-end and database.
+The specific set of APIs are exposed to the UI such that only the responses and requests made by the UI would be routed for operations.
+For storing and retrieving of data from the database, it uses Flex.Query Processor Library to execute SQL statements to a MySQL instance.
+The server also stores and execute the algorithm logic for registration and login authentication.
 
@@
         \begin{enumerate}
-        \item User signs up with an email  
-        \item UI generates fignerprint hash  
-        \item UI sends fingerprint hash and email of the registering user to backend  
-        \item UI displays the fingerprint hash to user  
-        \item Backend stores fingerprint hash and email into the database  
+            \item User signs up with an email and select a security level (Figure \ref{fig:regis})
+            \item UI generates device fingerprint JSON object containing 27 device components
+            \item UI sends device fingerprint and email of the registering user to backend server  
+            \item UI displays the table of 27-component device fingerprint to user (Figure \ref{fig:fingerprint-comp})
+            \item Backend stores device fingerprint and email into MySQL database
         \end{enumerate}
@@
             \item User logs in with email  
-        \item UI generates fingerprint hash  
-        \item UI sends fingerprint hash and email to backend  
-        \item Backend checks whether there exists any record for the pair of information and returns either true or false to authenticate the user  
-        \item UI prompts login success / failure  
+            \item UI generates device fingerprint JSON object containing 27 device components
+            \item UI sends device fingerprint and email to backend server
+            \item Backend checks whether there exists any record for email and runs an algorithm to match each of the 27 device fingerprint components based on the security level chosen by the user
+            \item  UI redirects to a login success page if email and device fingerprint were successfully matched.
+Otherwise, UI redirects to a login failure page if either email or device fingerprint failed to match
         \end{enumerate}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{assets/ui.png}
-    \caption{UI for the Web Applicaiton}
-    \label{fig:ui}
+    \includegraphics[width=0.5\textwidth]{assets/fig1-ui-threshold-level.png}
+    \caption{Registration Page}
+    \label{fig:regis}
 \end{figure}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/fig2-ui-fingerprint-components.png}
+    \caption{Demo Page to Show User Fingerprint Value}
+    \label{fig:fingerprint-comp}
+\end{figure}
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=0.5\textwidth]{assets/ui.png}
+%     \caption{UI for the Web Applicaiton}
+%     \label{fig:ui}
+% \end{figure}
 

### 2018-11-16 paper.tex
Removed 'hash' from conclusion

@@
 \section{Conclusion}
-In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique hashed fingerprints.
+In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique fingerprints.
 
-By combining various components of a device's properties, we could increase the fingerprint entropy as well as obtain a hash unqiue for an individual's device, correspondingly unique to an individual.
+By combining various components of a device's properties, we could increase the fingerprint entropy for an individual's device, correspondingly unique to an individual.
 

### 2018-11-16 paper.tex
Capitalize title
Update paper.tex
Co-Authored-By: githubxxcc <xuchen727@hotmail.com>

@@
 
-\title{Device fingerprinting for user authentication in web applications
+\title{Device Fingerprinting for User Authentication in Web Applications
 \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
 The authentication algorithm introduces a degree of complexity whereby the similarity of two device fingerprints is evaluated based on a threshold level.
-This threshold level is customizable during registration (Figure \ref{fig:level}) and explained in the table below.
+This threshold level is customizable during registration and the different levels are explained in Figure \ref{fig:level}.
 

### 2018-11-16 paper.tex
Integrated Keith's (#8)
* Added fingerprint as sole auth method discussion

* Integreated Keith's

* Added PDF for online review

* Removed 'hash' from conclusion

* Capitalize title

* Rebuilt pdf

* Update paper.tex

Co-Authored-By: githubxxcc <xuchen727@hotmail.com>

* Update paper.tex

Co-Authored-By: githubxxcc <xuchen727@hotmail.com>
FINAL

@@
 
-\title{Device Fingerprinting for User Authentication in Web Applications
-\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
+\title{Device Fingerprinting for User Authentication in Web Applications}
 %%%  \subtitle{[Extended Abstract]
@@
 
-The front-end user interface that displays the registration and login pages was built with Angular 6.0, designed with Material Design Bootstrap for a consistent and fluent design.
+The front-end user interface that displays the registration and login pages was built with Angular 6.0, designed with Material Design Bootstrap for a consistent and fluent design (Figure \ref{fig:login}.
 Background animation was added to create an aesthetic appeal that blends into the “security” theme.
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/fig4-ui-authentication.png}
+    \caption{Demo Web App UI}
+    \label{fig:login}
+\end{figure}
 The NodeJS server utilizes Express 4.0 for communication of data between front-end and database.
@@
 For storing and retrieving of data from the database, it uses Flex.Query Processor Library to execute SQL statements to a MySQL instance.
-The server also stores and execute the algorithm logic for registration and login authentication.
+The server also stores and executes the algorithm logic for registration and login authentication.
 
